| Base de datos de abejas Ibéricas \n| Iberian Bees database\n

### 2022-03-17 Manuscript/manuscript.Rmd
edits on ms

```{r Tabla1, results='asis', echo=FALSE, cache=FALSE}
library("knitr")
metadata <- read.csv("../Data/Metadata/attributes.csv")
colnames(metadata) <- c("Variable name", "Description", "Data type")

@@

```{r Fig1, echo=FALSE, fig.align='center', out.width="70%", fig.cap="\\label{fig:Fig1} Barplot indicating the 20 more common recorded species in the final data set."}
# Prepare top 20 records
top_20 <- data %>%
  filter(!Accepted_name == "Apis mellifera") %>%
  group_by(Accepted_name) %>%
  summarise(no_rows = length(Accepted_name)) %>%
  arrange(-no_rows) %>%
  slice(1:20)
# Fix row position
top_20$Accepted_name <- factor(top_20$Accepted_name, levels = top_20$Accepted_name)
# Plot
ggplot(top_20, aes(x = Accepted_name, y = no_rows)) +
  geom_bar(stat = "identity", fill = "#287D8EFF") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8, face = "italic")) +
  ylab("Number of records") +
  xlab("Species") +
  scale_y_continuous(expand = c(0, 0))
```

```{r Fig2, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Map of the Iberian peninsula indicating where the bee occurrences were sampled.",out.width="70%"}
# code courtesy of Paco Rodriguez.
library(sf)
library(raster)
library(rasterVis)
library(tidyverse)
crs.geo <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
crs.laea <- "+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs"

@@

```{r Fig3, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Cobertura temporal de (A) los años con más ocurrencias, y (B) los meses con más ocurrencias. ", message=FALSE, warning=FALSE, cache=FALSE}
# Prepare top 20 records
by_year <- data %>% filter(!Accepted_name == "Apis mellifera")

>>>>

```{r Tabla1, results='asis', echo=FALSE, cache=FALSE}
library("knitr")
metadata <- read.csv("../Data/Metadata/attributes.csv")
colnames(metadata) <- c("","Variable name", "Description", "Data type")

@@

```{r echo=FALSE, fig.align='center', out.width="70%", fig.cap="Figure 1"}
# Prepare top 20 records
top_20 <- data %>%
  filter(!Accepted_name == "Apis mellifera") %>%
  group_by(Accepted_name) %>%
  summarise(no_rows = length(Accepted_name)) %>%
  arrange(-no_rows) %>%
  slice(1:20)
# Fix row position
top_20$Accepted_name <- factor(top_20$Accepted_name, levels = top_20$Accepted_name)
# Plot
ggplot(top_20, aes(x = Accepted_name, y = no_rows)) +
  geom_bar(stat = "identity", fill = "#287D8EFF") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8, face = "italic")) +
  ylab("Number of records") +
  xlab("Species") +
  scale_y_continuous(expand = c(0, 0))
```

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Figure 2",out.width="70%"}
# code courtesy of Paco Rodriguez.
library(sf)
library(raster)
library(rasterVis)
library(tidyverse)
crs.geo <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
crs.laea <- "+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs"

@@

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 3", message=FALSE, warning=FALSE, cache=FALSE}
# Prepare top 20 records
by_year <- data %>% filter(!Accepted_name == "Apis mellifera")
